---
title: "Contagion Overview by US State"
author: "Jeff Renz, Brian Liberatore"
date: "`r Sys.Date()`"
output: 
  powerpoint_presentation: 
    reference_doc: templates/PASS_Template.potx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warn=-1)
#options(warn=-1)
```

```{r LoadData, echo=FALSE, warning=FALSE, message=FALSE}
source("scripts/00_load_libraries.R")
source("scripts/01_load_data.R")
source("scripts/02_load_functions.R")
```

# States most impacted by COVID-19
```{r States_overview, warning = FALSE, message = FALSE, echo=FALSE, fig.width=12}
State <- as.factor(state.name[match(data$state, state.abb)])


state_summary <- data %>%
  cbind(State) %>%
  group_by(State, date) %>%
  summarise("Total Cases" = sum(cases), "Total Deaths" = sum(deaths)) %>%
  group_by(State) %>%
  summarize("Total Cases" = max(`Total Cases`),"Total Deaths" = max(`Total Deaths`)) %>%
  arrange(desc(`Total Cases`)) %>%
  head(15)

state_summary$`Total Cases` <- comma(state_summary$`Total Cases`)
state_summary$`Total Deaths` <- comma(state_summary$`Total Deaths`)

kable(state_summary)

```

# `r state.name[6]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}

state_chart_function(state.abb[6])

```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[6])
```
:::
::::::::::::::
# `r state.name[1]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[1])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[1])
```
:::
::::::::::::::
# `r state.name[1]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[1])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[1])
```
:::
::::::::::::::
# `r state.name[2]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[2])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[2])
```
:::
::::::::::::::
# `r state.name[2]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[2])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[2])
```
:::
::::::::::::::
# `r state.name[3]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[3])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[3])
```
:::
::::::::::::::
# `r state.name[3]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[3])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[3])
```
:::
::::::::::::::
# `r state.name[4]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[4])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[4])
```
:::
::::::::::::::
# `r state.name[4]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[4])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[4])
```
:::
::::::::::::::
# `r state.name[5]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[5])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[5])
```
:::
::::::::::::::
# `r state.name[5]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[5])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[5])
```
:::
::::::::::::::
# `r state.name[6]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[6])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[6])
```
:::
::::::::::::::
# `r state.name[6]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[6])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[6])
```
:::
::::::::::::::
# `r state.name[7]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[7])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[7])
```
:::
::::::::::::::
# `r state.name[7]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[7])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[7])
```
:::
::::::::::::::
# `r state.name[8]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[8])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[8])
```
:::
::::::::::::::
# `r state.name[8]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[8])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[8])
```
:::
::::::::::::::
# `r state.name[9]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[9])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[9])
```
:::
::::::::::::::
# `r state.name[9]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[9])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[9])
```
:::
::::::::::::::
# `r state.name[10]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[10])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[10])
```
:::
::::::::::::::
# `r state.name[10]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[10])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[10])
```
:::
::::::::::::::
# `r state.name[11]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[11])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[11])
```
:::
::::::::::::::
# `r state.name[11]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[11])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[11])
```
:::
::::::::::::::
# `r state.name[12]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[12])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[12])
```
:::
::::::::::::::
# `r state.name[12]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[12])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[12])
```
:::
::::::::::::::
# `r state.name[13]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[13])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[13])
```
:::
::::::::::::::
# `r state.name[13]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[13])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[13])
```
:::
::::::::::::::
# `r state.name[14]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[14])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[14])
```
:::
::::::::::::::
# `r state.name[14]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[14])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[14])
```
:::
::::::::::::::
# `r state.name[15]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[15])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[15])
```
:::
::::::::::::::
# `r state.name[15]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[15])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[15])
```
:::
::::::::::::::
# `r state.name[16]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[16])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[16])
```
:::
::::::::::::::
# `r state.name[16]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[16])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[16])
```
:::
::::::::::::::
# `r state.name[17]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[17])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[17])
```
:::
::::::::::::::
# `r state.name[17]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[17])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[17])
```
:::
::::::::::::::
# `r state.name[18]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[18])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[18])
```
:::
::::::::::::::
# `r state.name[18]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[18])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[18])
```
:::
::::::::::::::
# `r state.name[19]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[19])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[19])
```
:::
::::::::::::::
# `r state.name[19]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[19])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[19])
```
:::
::::::::::::::
# `r state.name[20]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[20])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[20])
```
:::
::::::::::::::
# `r state.name[20]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[20])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[20])
```
:::
::::::::::::::
# `r state.name[21]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[21])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[21])
```
:::
::::::::::::::
# `r state.name[21]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[21])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[21])
```
:::
::::::::::::::
# `r state.name[22]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[22])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[22])
```
:::
::::::::::::::
# `r state.name[22]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[22])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[22])
```
:::
::::::::::::::
# `r state.name[23]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[23])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[23])
```
:::
::::::::::::::
# `r state.name[23]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[23])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[23])
```
:::
::::::::::::::
# `r state.name[24]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[24])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[24])
```
:::
::::::::::::::
# `r state.name[24]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[24])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[24])
```
:::
::::::::::::::
# `r state.name[25]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[25])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[25])
```
:::
::::::::::::::
# `r state.name[25]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[25])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[25])
```
:::
::::::::::::::
# `r state.name[26]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[26])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[26])
```
:::
::::::::::::::
# `r state.name[26]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[26])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[26])
```
:::
::::::::::::::
# `r state.name[27]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[27])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[27])
```
:::
::::::::::::::
# `r state.name[27]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[27])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[27])
```
:::
::::::::::::::
# `r state.name[28]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[28])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[28])
```
:::
::::::::::::::
# `r state.name[28]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[28])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[28])
```
:::
::::::::::::::
# `r state.name[29]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[29])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[29])
```
:::
::::::::::::::
# `r state.name[29]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[29])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[29])
```
:::
::::::::::::::
# `r state.name[30]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[30])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[30])
```
:::
::::::::::::::
# `r state.name[30]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[30])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[30])
```
:::
::::::::::::::
# `r state.name[31]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[31])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[31])
```
:::
::::::::::::::
# `r state.name[31]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[31])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[31])
```
:::
::::::::::::::
# `r state.name[32]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[32])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[32])
```
:::
::::::::::::::
# `r state.name[32]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[32])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[32])
```
:::
::::::::::::::
# `r state.name[33]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[33])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[33])
```
:::
::::::::::::::
# `r state.name[33]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[33])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[33])
```
:::
::::::::::::::
# `r state.name[34]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[34])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[34])
```
:::
::::::::::::::
# `r state.name[34]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[34])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[34])
```
:::
::::::::::::::
# `r state.name[35]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[35])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[35])
```
:::
::::::::::::::
# `r state.name[35]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[35])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[35])
```
:::
::::::::::::::
# `r state.name[36]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[36])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[36])
```
:::
::::::::::::::
# `r state.name[36]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[36])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[36])
```
:::
::::::::::::::
# `r state.name[37]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[37])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[37])
```
:::
::::::::::::::
# `r state.name[37]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[37])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[37])
```
:::
::::::::::::::
# `r state.name[38]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[38])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[38])
```
:::
::::::::::::::
# `r state.name[38]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[38])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[38])
```
:::
::::::::::::::
# `r state.name[39]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[39])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[39])
```
:::
::::::::::::::
# `r state.name[39]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[39])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[39])
```
:::
::::::::::::::
# `r state.name[40]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[40])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[40])
```
:::
::::::::::::::
# `r state.name[40]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[40])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[40])
```
:::
::::::::::::::
# `r state.name[41]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[41])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[41])
```
:::
::::::::::::::
# `r state.name[41]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[41])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[41])
```
:::
::::::::::::::
# `r state.name[42]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[42])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[42])
```
:::
::::::::::::::
# `r state.name[42]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[42])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[42])
```
:::
::::::::::::::
# `r state.name[43]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[43])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[43])
```
:::
::::::::::::::
# `r state.name[43]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[43])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[43])
```
:::
::::::::::::::
# `r state.name[44]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[44])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[44])
```
:::
::::::::::::::
# `r state.name[44]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[44])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[44])
```
:::
::::::::::::::
# `r state.name[45]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[45])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[45])
```
:::
::::::::::::::
# `r state.name[45]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[45])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[45])
```
:::
::::::::::::::
# `r state.name[46]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[46])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[46])
```
:::
::::::::::::::
# `r state.name[46]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[46])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[46])
```
:::
::::::::::::::
# `r state.name[47]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[47])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[47])
```
:::
::::::::::::::
# `r state.name[47]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[47])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[47])
```
:::
::::::::::::::
# `r state.name[48]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[48])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[48])
```
:::
::::::::::::::
# `r state.name[48]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[48])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[48])
```
:::
::::::::::::::
# `r state.name[49]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[49])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[49])
```
:::
::::::::::::::
# `r state.name[49]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[49])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[49])
```
:::
::::::::::::::
# `r state.name[50]`
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
state_chart_function(state.abb[50])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
state_map_function(state.abb[50])
```
:::
::::::::::::::
# `r state.name[50]` infection statistics
:::::::::::::: {.columns}
::: {.column}
```{r echo=FALSE, message=FALSE, warning=FALSE}
key_figures(state.abb[50])
```
:::
::: {.column}
```{r echo=FALSE,message=FALSE,warning=FALSE}
percent_change_chart(state.abb[50])
```
:::
::::::::::::::




